\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{mathptmx} % Times New Roman font
\usepackage{array}

% Metadata
\hypersetup{
    pdftitle={Salomon Santiago Esquivel - Data Analyst Resume},
    pdfauthor={Salomon Santiago Esquivel},
    pdfsubject={Data Analyst Resume},
    pdfkeywords={Data Analyst, SQL, Tableau, Excel, Python, ETL, Data Modeling, MongoDB, Salesforce, R, Power BI, Data Visualization, Business Intelligence, Statistical Analysis, Data Mining, Dashboards, KPIs, Metrics, Database Management, Data Warehousing, Reporting, Analytics, Machine Learning, Predictive Analytics, Data Science, Big Data, Cloud Computing, AWS, Azure, Google Cloud, Snowflake, Apache Spark, Hadoop, Pandas, NumPy, Matplotlib, Seaborn, Jupyter, Git, A-B Testing, Hypothesis Testing, Regression Analysis, Time Series Analysis, Data Governance, Data Quality, Data Pipeline, Data Engineering, Cross-functional Collaboration, Stakeholder Management, Business Acumen, Problem Solving, Critical Thinking, Communication Skills, Presentation Skills, Project Management, GitHub, Portfolio, IBM Data Analyst, Available Immediately},
    colorlinks=false,
    pdfborder={0 0 0}
}

% Formatting
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Section formatting
\titleformat{\section}
  {\Large\bfseries}
  {}
  {0em}
  {}
  [\titlerule]
\titlespacing*{\section}{0pt}{1.5ex plus 1ex minus .2ex}{1ex plus .2ex}

\titleformat{\subsection}
  {\large\bfseries}
  {}
  {0em}
  {}

% List formatting
\setlist{noitemsep, topsep=0em, partopsep=0em}
\setlist[itemize]{leftmargin=1.8em, itemindent=0em}

\begin{document}

% Header
\begin{center}
{\Huge\bfseries Salomón Santiago Esquivel}\\[0.2em]
{\large 
Email: \href{mailto:salo.santiago96@gmail.com}{salo.santiago96@gmail.com} $\mid$ 
LinkedIn: \href{https://linkedin.com/in/salomon-santiago-493002a7/}{salomon-santiago-493002a7} $\mid$ 
Portfolio: \href{https://salo996.github.io/Data-analyst-portfolio/}{salo996.github.io/Data-analyst-portfolio} $\mid$ 
Location: Mexico City $\mid$ Phone: +52 551916 4142
}
\end{center}

\vspace{0.2em}

\section{Summary}
Results-driven Data Analyst with 6+ years of experience converting complex datasets into strategic business insights. Proficient in SQL, Python, Excel, Tableau, and pipeline optimization, with a proven track record of boosting operational efficiency by 20\%. Strong collaborator who partners with cross-functional teams to drive informed decision-making. Currently advancing technical skills through IBM Data Analyst Professional Certificate.

\section{Technical Skills}
\begin{itemize}
  \item \textbf{Programming \& Analysis:} Python, SQL, Excel (Advanced), Tableau
  \item \textbf{Databases:} Salesforce, MongoDB
  \item \textbf{Data Processes:} ETL, Data transformation, Data modeling, Data visualization
  \item \textbf{Tools:} Microsoft Office Suite, Jira, GitHub, Jupyter Notebooks
  \item \textbf{Languages:} English (Fluent), Spanish (Native)
\end{itemize}

\section{Work Experience}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Service Offering Manager – North America} & \textbf{Lenovo (Feb 2022 – Jul 2025)} \\
\end{tabular*}
\begin{itemize}
  \item Increased operational efficiency by 20\% through systematic analysis and data-driven improvements.
  \item Improved customer satisfaction by 25\% via quarterly data analysis for portfolio optimization.
  \item Streamlined custom offering creation using optimized data models, significantly reducing time-to-market.
  \item Established comprehensive data governance standards with 100\% team adoption.
\end{itemize}

\vspace{0.9em}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Claims Examiner – LATAM} & \textbf{Swiss Re (Mar 2020 – Jan 2022)} \\
\end{tabular*}
\begin{itemize}
  \item Enhanced claims processing efficiency by 13\% through optimized communication workflows.
  \item Reduced denied claims by 15\% through improved document analysis processes.
  \item Increased financial data accuracy by 25\% with enhanced bordereau analysis.
  \item Managed complex data ETL processes to deliver accurate financial reporting.
\end{itemize}

\vspace{0.9em}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{FP\&A Finance Intern ITO – LATAM} & \textbf{General Electric (Aug 2018 – Feb 2020)} \\
\end{tabular*}
\begin{itemize}
  \item Improved financial data accuracy by 20\% via detailed analysis of Salesforce reports.
  \item Increased sales data quality by 15\% through collaboration with sales leadership.
  \item Optimized data pipelines, enhancing documentation processing efficiency by 85\%.
\end{itemize}

\vspace{0.9em}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Controller Intern} & \textbf{Mira Companies (May 2017 – Aug 2018)} \\
\end{tabular*}
\begin{itemize}
  \item Increased accounts payable efficiency by 20\% through ERP system implementation.
  \item Automated payment processing workflows, achieving a 20\% time savings.
\end{itemize}

\section{Certifications \& Projects}
\begin{itemize}
  \item IBM Data Analyst Professional Certificate (In Progress)
  \item Google Data Analytics Certificate (Coursera)
  \item SQL, Excel for Data Analysis, MongoDB (Codecademy)
  \item IELTS Academic
  \item \textbf{Portfolio Projects:} Sales Performance Analysis, E-commerce Analytics, Customer Behavior Analysis featuring SQL, Python, and interactive dashboards
\end{itemize}

\section{Education}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Universidad Iberoamericana, Mexico City} & \textbf{Bachelor of Engineering in Industrial Engineering} \\
\end{tabular*}
\begin{itemize}
  \item Relevant Coursework: Statistics, Data Analysis, Process Optimization
  \item Track and Field Team Member (2016–2018)
\end{itemize}

\end{document}